Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-29 manuscript/supplemental_material.Rnw
remove the GO acronym from supplemental

\begin{table}
\footnotesize
<<go.analysis,warning=FALSE,message=FALSE,echo=FALSE,results="asis">>=
placenta.go.results <- rbindlist(list(head(n=20,placenta_go_results_mf[classic.fdr < 0.05,]),
                             head(n=20,placenta_go_results_bp[classic.fdr < 0.05,])))
placenta.go.results <- placenta.go.results[,Annotated:=NULL]
setnames(placenta.go.results,"Significant","# Core")
setnames(placenta.go.results,"classic","p value")
setnames(placenta.go.results,"classic.fdr","FDR")
setnames(placenta.go.results,"GO.ID","GO ID")
setnames(placenta.go.results,"Term","GO Term")
print(xtable(placenta.go.results,
             digits=2,
             display=c("d","s","s","d","f","e","e","s")),
      include.rownames=FALSE,
      booktabs=TRUE,
      floating=FALSE
      )
@ 
\caption{\ac{GO} terms most significantly enriched
  (\Sexpr{placenta.go.results[,sum(Ontology=="MF")]} MF,
  \Sexpr{placenta.go.results[,sum(Ontology=="BP")]} BP)
  in the core placenta transcriptome as compared to all genes
  with 1:1 human orthologs in all species. “\# Core” is the
  number of genes in the core transcriptome for each \ac{GO} term;
  “Expected” is the number of genes expected in the core
  transcriptome for each term; “p-value” are the odds of this
  occurring by chance calculated by the Fisher exact test for
  each term; “FDR” is the false discovery rate as estimated by
  the Benjamini and Hochberg procedure \cite{Benjamini1995:bh_procedure}.}
\label{tab:core_placenta_go_terms}
\end{table}

>>>>

\begin{table}
\footnotesize
<<go.analysis,warning=FALSE,message=FALSE,echo=FALSE,results="asis">>=
placenta.go.results <- rbindlist(list(head(n=20,placenta_go_results_mf[classic.fdr < 0.05,]),
                             head(n=20,placenta_go_results_bp[classic.fdr < 0.05,])))
placenta.go.results <- placenta.go.results[,Annotated:=NULL]
setnames(placenta.go.results,"Significant","# Core")
setnames(placenta.go.results,"classic","p value")
setnames(placenta.go.results,"classic.fdr","FDR")
setnames(placenta.go.results,"GO.ID","GO ID")
setnames(placenta.go.results,"Term","GO Term")
print(xtable(placenta.go.results,
             digits=2,
             display=c("d","s","s","d","f","e","e","s")),
      include.rownames=FALSE,
      booktabs=TRUE,
      floating=FALSE
      )
@ 
\caption{GO terms most significantly enriched
  (\Sexpr{placenta.go.results[,sum(Ontology=="MF")]} MF,
  \Sexpr{placenta.go.results[,sum(Ontology=="BP")]} BP)
  in the core placenta transcriptome as compared to all genes
  with 1:1 human orthologs in all species. “\# Core” is the
  number of genes in the core transcriptome for each GO term;
  “Expected” is the number of genes expected in the core
  transcriptome for each term; “p-value” are the odds of this
  occurring by chance calculated by the Fisher exact test for
  each term; “FDR” is the false discovery rate as estimated by
  the Benjamini and Hochberg procedure \cite{Benjamini1995:bh_procedure}.}
\label{tab:core_placenta_go_terms}
\end{table}
